Databases are an effective and efficient method for storage and access of mass-spectrometry data

### 2025-06-11 manuscript/manuscript.Rmd
Moving supplement to end

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, include=FALSE, eval=TRUE)
library(tidyverse)
library(ggtext)
library(patchwork)

@@

1. Is there a simple database schema that enables exploratory MS queries with basic SQL statements?
2. How expensive in time and (disk) space is it to access MS data in SQLite, DuckDB, and Parquet formats?
3. How does this cost compare to more complex formats that have been previously proposed?

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, include=FALSE, eval=FALSE)
library(tidyverse)
library(ggtext)
library(patchwork)

@@

1. Is there a simple database schema that enables exploratory MS queries with basic SQL statements?
2. How expensive in time and (disk) space is it to access MS data in SQLite, DuckDB, and Parquet formats?
3. How does this cost compare to more complex MS storage formats that have been previously proposed?
